Behavior Driven Development in Haskell

### 2012-06-03 paper.tex
Minor wording change
State, that the solution section describes "automatic spec discovery"
Consistency

We propose to use Doctest and Haddock for evidence that is useful as
user documentation, and Hspec for evidence that is not useful as user
documentation.  The following subsections discuss problems that we
have to solve before we can do this.

@@

As we explained in Section~\ref{sec:problem},
we use Doctest for user documentation and Hspec for code documentation.
The following subsections explain two extensions to Haddock's markup.
Subsequently, combinators for expectations, that can be used with
Hspec, are introduced.

@@

\begin{itemize}
\item Add markup syntax for interactive examples to Haddock
\item Add markup syntax for properties to Haddock
\item
    Implement a tool, similar to Python's {\tt doctest} module, that
    can verify examples and test properties in Haddock comments.
    The implementation is discussed in Section~\ref{sec:doctest}.

@@

\noindent To specify properties, we also introduce new markup. A line
starting with ``{\tt prop>}'' indicates a property.

>>>>

We propose to use Doctest and Haddock for evidence that is useful as
user documentation, and Hspec for evidence that is not useful as user
documentation.  The following subsections discuss problems that we
have to solve before we can do so.

@@

As we explained in Section~\ref{sec:problem},
we use Doctest for user documentation and Hspec for code documentation.
The following subsections explain two extensions to Haddock's markup.
Subsequently, combinators for expectations, that can be used with
Hspec, are introduced.
And a mechanism for automatic spec discovery is described.

@@

\begin{itemize}
\item Add markup syntax for interactive examples to Haddock.
\item Add markup syntax for properties to Haddock.
\item
    Implement a tool, similar to Python's {\tt doctest} module, that
    can verify examples and test properties in Haddock comments.
    The implementation is discussed in Section~\ref{sec:doctest}.

@@

\noindent To specify properties, we also introduce new markup. A line
starting with ``{\tt prop>}'' indicates a property:
